---
title: "Financial Modeling - Amazon"
author: "Kevin Mendonsa"
date: "November 13, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```





## Unit 11: Modeling Financial Data


### Install required packages

- install.packages("tseries")

- install.packages("fpp")


### Load the libraries

```{r load_libraries}
library(tseries)

library(fpp)
```

### S&P 500 (^GSPC)
####    SNP - SNP Real Time Price. Currency in USD

### TODO: Download the data of SP500 '^gspc'.

```{r get_stock_data}
SNPdata <- get.hist.quote("amzn",quote="Close")
```

### Calculate the log returns, which is the subtraction of log(lag(SNPdata)) and log(SNPdata)

```{r log_returns}
SNPret <- log(lag(SNPdata)) - log(SNPdata)
```

### Calculate volatility measure that is to multiply sd(SNPret),sqrt(250), 100
#### 250 is the number of days the stock market is open in a year

```{r volatility_measure}
SNPvol <- sd(SNPret) * sqrt(250) * 100
```

### Define getVol function for volatility

```{r create_getVol_function}
getVol <- function(d, logrets) {
                              	var = 0
                              	lam = 0
                              	varlist <- c()
                              
                              	for (r in logrets) {
                                                		lam = lam*(1 - 1/d) + 1
                                                	  var = (1 - 1/lam)*var + (1/lam)*r^2
                                                		varlist <- c(varlist, var)
                                                	 }
                              
                              	sqrt(varlist)
                              }
```


### Calculate volatility over entire length of series for three different decay factors: 10, 30, 100

### Call the getVol function with the parameters: 10,SNPret

```{r decay_factor_10}
volest <- getVol(10,SNPret)
```


### TODO: call getVol function with the parameters: 30,SNPret

```{r decay_factor_30}
volest2 <- getVol(30,SNPret)
```

### TODO: call getVol function with the parameters: 100,SNPret

```{r decay_factor_100}
volest3 <- getVol(100,SNPret)
```

### Plot the results, overlaying the volatility curves on the data.

```{r plot_volatility_curve}
plot(volest,type="l")
```

### Add connected line segments for volest2 with the parameters: type="l",col="red"

```{r add_decay_30_line}
plot(volest,type="l")
lines(volest2, type="l", col="red")
```

### Add connected line segments for volest3 with the parameters: type="l",col="blue"

```{r add_decay_100_line}
plot(volest,type="l")
lines(volest2, type="l", col="red")
lines(volest3, type="l", col="blue")
```

